


### Time dynamics of most common words (*full corpus*)

```{r time_corpus , echo=FALSE,  message = FALSE, warning = FALSE, fig.height=6}

korpus_words %>%
  mutate(Datum = floor_date(dejt, "quarter")) %>% 
  group_by(Datum) %>%
  count(word) %>% 
  mutate(gn = sum(n)) %>% 
  filter(word %in% rijeci_korelacija) %>%
  mutate(word = recode(word,
                       'sigurnost' = "Safety",
                       'zakon' = "Law",
                       "uber" = "Uber",
                       "vozila"  = "Vehicles",
                       "zakona" = "Law",
                       "dozvola"  = "Taxi licence" ,
                       "konkurencija" = "Competition",
                       "nelegalno" = "Illegal",
                       "zarada" = "Profit")) %>%
  ggplot(., aes(Datum, n / gn)) + 
  geom_point() +
  geom_smooth() +
  facet_wrap(~ word, scales = "free_y") +
  scale_y_continuous(labels = scales::percent_format()) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  #scale_x_date(labels = date_format("%Y %m")) +
  labs(title="",
       x ="Date", y = "% of total words(quarterly)")



```



---
  layout: false
class: middle, inverse

# RESULTS AND DISCUSSION
---
  
  layout: true
# RESULTS AND DISCUSSION
---
  <br>
  ## Corpus conflict (unigrams)
  <br>
```{r unigram_Words_conflict,  echo=FALSE, fig.height=7}

#uber_words %>% 
# count(word) %>%
#  arrange(desc(n)) %>%
#  top_n(30) -> uber_corpus

#kable(uber_corpus,
#                        caption = "Najčešće riječi u UBER korpusu") %>%
#  kable_styling() %>%
#  scroll_box(width = "500px", height = "300px")


sukob_words %>% 
  count(word) %>%
  arrange(desc(n)) %>%
  mutate(ratio = (n / sum(n))*100) %>%
  mutate(ratio = round(ratio,2)) %>%
  mutate(ratio = paste0(ratio,"%")) %>%
  filter(n > 100) %>%
  mutate(Word = recode(word,
                       'sigurnost' = "safety",
                       'zakona' = "law",
                       "uber" = "uber",
                       "vozila"  = "vehicles",
                       'taksisti' = "taxi drivers",
                       'taksista' = "taxi drivers")) %>%
  distinct(.,Word,.keep_all = T) %>%
  rename( N = n, Ratio = ratio) %>%
  select(Word,N,Ratio) %>%
  slice(-1)-> sukob_corpus



kable(sukob_corpus) %>% # ,caption = "Table X: Most frequent words (>100)"
  kable_styling() 

```

-
  
  ---
  
  layout: true
# RESULTS AND DISCUSSION
---
  
  ### Most correlated words (*with selected important words from corpus "conflict"*)
  
```{r parwiseCount_conflict, echo=FALSE,  message = FALSE, warning = FALSE, fig.height=6}

###PARWISE COUNT###

# prikazuju se samo tri riječi prve

sukob_words %>%
  select(idClanka, word, sukob) %>%
  pairwise_count(word, idClanka, sort = TRUE) -> sukob_word_pairs


# sukob_words %>%
#  select(sukob, word) %>%
#  mutate(sukob = case_when(sukob == "trad" ~ 1,
#            sukob == "kont" ~ 2,
#            sukob == "kont2" ~3,
#            sukob == "repo" ~ 4)) %>%
#  mutate(sukob = as.integer(sukob)) %>% #str()
#  pairwise_count(word, sukob, sort = TRUE) -> sukob_word_pairs_sukob


sukob_rijeci <- c("prijedlog", "prosvjed", "prijetnje", "napad" ) # šteta
uber_rijeci <- c("posao", "zarada", "koristi", "cijena", "plaćanje")
korpus_rijeci <- c("zakon", "nelegalno", "politika", "ministar","turizam", "sigurnost")

##PARWISE COUNT SA IZABRANIM RIJEČIMA##



sukob_word_pairs %>%
  filter(item2 %in% sukob_rijeci) %>% 
  group_by(item2) %>%
  slice(1:8) %>%
  ungroup() %>%
  slice(c(-2,-4,-6,-11,-19,-24,-28)) %>%
  mutate(item1 = recode(item1,
                        'prijevoza' = "transport",
                        'taksisti' = "taxi drivers",
                        "uber" = "uber",
                        "taksista" = "taxi drivers",
                        "vozila"  = "vehicles",
                        "zakona" = "law"  ,
                        "kuna"  = "kuna" ,
                        "prijevoz" = "transport",
                        "zagrebu" = "zagreb",
                        "prometa" = "traffic" ,
                        "vozaea" = "drivers",
                        "uberu" = "uber" ,
                        "usluga" = "service",
                        "mora" = "must",
                        "može" = "can",
                        "prijevoza" = "traffic",
                        "uberu" = "uber",
                        "smatraju" = "consider",
                        "protiv" = "against",
                        "kažu" = "claim",
                        "prijevozu" = "traffic",
                        "tržište" = "market",
                        "imaju" = "have",
                        "grada" = "city",
                        "hrvatske" = "Croatia",
                        "mogu" = "possibility",
                        "infrastrukture" = "infrastructure")) %>%
  mutate(item2 = recode(item2,
                        'napad' = "Attack",
                        'prijedlog' = "Suggestion",
                        "prijetnje" = "Threats",
                        "prosvjed"  = "Demonstrations" )) %>%
  mutate(item2 = reorder(item2, n)) %>%
  ggplot(aes(item1, n)) +
  geom_bar(stat = "identity") +
  facet_wrap(~ item2, scales = "free") +
  coord_flip() +
  labs(title="",
       x ="Word", y = "Number of words") 

```


---
  
  layout: true
# RESULTS AND DISCUSSION
---
  
  
  ### Most important terms through time (*quarterly;corpus conflict*). 
  
  
  
```{r, eval=FALSE, echo=FALSE,  message = FALSE, warning = FALSE }
uber_words %>%
  mutate(Datum = floor_date(dejt, "quarter")) %>% 
  group_by(Datum) %>%
  count(word) %>% 
  mutate(gn = sum(n)) %>% 
  filter(word %in% uber_rijeci) %>%
  ggplot(., aes(Datum, n / gn)) + 
  geom_point() +
  ggtitle("Korpus Uber") +
  geom_smooth() +
  facet_wrap(~ word, scales = "free_y") +
  scale_y_continuous(labels = scales::percent_format())


korpus_words %>%
  mutate(Datum = floor_date(dejt, "quarter")) %>% 
  group_by(Datum) %>%
  count(word) %>% 
  mutate(gn = sum(n)) %>% 
  filter(word %in% korpus_rijeci) %>%
  ggplot(., aes(Datum, n / gn)) + 
  geom_point() +
  ggtitle("Korpus") +
  geom_smooth() +
  facet_wrap(~ word, scales = "free_y") +
  scale_y_continuous(labels = scales::percent_format())


```


---
  layout: false
class: middle, inverse

# TOPIC ANALYSIS
---
  layout: true
# TOPIC ANALYSIS

---
  
```{r IDF,echo=FALSE,  message=FALSE, warning=FALSE, fig.height=7}


sukob_words %>%
  count(sukob, word, sort = TRUE) %>%
  bind_tf_idf(word, sukob, n) -> idf_sukob

options(scipen = 1000000)
idf_sukob %>%
  mutate(word = factor(word, levels = rev(unique(word)))) %>% 
  group_by(sukob) %>% 
  select(sukob, word, tf_idf) %>%
  arrange(desc(tf_idf)) %>% 
  do(head(., n = 5)) %>% 
  filter(!word %in% c("tremac", "davor", "nekih", "ovdje",
                      "franković", "grabar", "kitarović",
                      "trebao", "martina", "ivan", "ribić", "pilko"))   %>%
  mutate(word = recode(word,
                       'dojam' = "impression",
                       'korisne' = "usefull",
                       "ispitanih" = "surveyed",
                       "odgovorilo" = "answered",
                       "policijskoj"  = "police",
                       "prijetnjama" = "threats"  ,
                       "regulativa"  = "regulation" ,
                       "verbalnom" = "verbal",
                       "žale" = "complain",
                       "napada" = "attack" ,
                       "dubrovačko" = "dubrovnik",
                       "nasilja" = "violence" ,
                       "usluga" = "service",
                       "opasnost" = "danger",
                       "partnerima" = "partners",
                       "pozitivna" = "positive",
                       "prošlih" = "historic",
                       "relikt" = "relict",
                       "štete" = "damage",
                       "prijedloga" = "proposal",
                       "naknadu" = "compensation",
                       "zakone" = "law",
                       'cestama' = "road",
                       'provodi' = "implement",
                       "pismu" = "letter",
                       "predstavnike" = "representative",
                       "primjedbi"  = "complaints",
                       "usluga" = "service"  ,
                       "ovlasti"  = "authority" ,
                       "umjesto" = "insteda",
                       "direktive" = "directives",
                       "dodatne" = "additional" ,
                       "dovodi" = "bring",
                       "interesu" = "interest" ,
                       'izvješća' = "report",
                       'mirnim' = "peacefull",
                       "prekršajni" = "criminal",
                       "općine" = "county",
                       "italiji"  = "italy",
                       "propisano" = "prescribed"  ,
                       "visoki"  = "high" ,
                       "usluga" = "service",
                       "javni" = "public",
                       "prijedloga" = "suggestion" ,
                       "optužni" = "indictment",
                       "prijavu" = "notification" ,
                       "list" = "paper",
                       "odbio" = "revoke",
                       "večernji" = "night",
                       'inspekcija' = "inspection",
                       'prijedlog' = "suggestion",
                       "aplikacija" = "application",
                       "troškovi" = "costs",
                       "napad"  = "attack",
                       "gotovo" = "over"  ,
                       "automobil"  = "car" ,
                       "sati" = "hours",
                       "policiji" = "police",
                       "potom" = "after" ,
                       "staklo" = "glass",
                       "ubacili" = "throw into" ,
                       "institucijama" = "institutions",
                       'normalno' = "normal",
                       'potpredsjednik' = "vice president",
                       "spontano" = "spontaneous",
                       "taxija" = "taxi",
                       "automobilu"  = "car" )) %>%
  ggplot(.,aes(reorder(word,tf_idf), tf_idf, fill = sukob)) +
  geom_col(show.legend = FALSE) +
  theme(axis.text.y = element_text(angle = 30, hjust = 1, size = 8)) +
  facet_wrap(~sukob, ncol = 2, scales = "free") +
  coord_flip() +
  labs(title="",
       x ="Word", y = "TF-IDF statistic") -> gg_idf_1

gg_idf_1

```


---
  layout: false
class: middle, inverse

# SENTIMENT ANALYSIS
---
  layout: true
# SENTIMENT ANALYSIS

---
  
  
  <br>
  ## Full text corpus
  <br>
  
```{r sentiment, echo=FALSE,  message = FALSE, warning = FALSE, fig.height=5 }

##SENTIMENT_FUNKCIJA

izracunaj_sentiment <- function(dataset) {
  
  dataset %>%
    inner_join( Crosentilex_sve, by = "word") %>%
    mutate(word = gsub("\\d+", NA, word)) %>%
    mutate(word = gsub("^[a-zA-Z]$", NA, word)) %>%
    filter(!is.na(word)) %>%
    select(word, brija, dejt, sentiment) %>% 
    unique() %>%
    spread(. , brija, sentiment) %>%
    mutate(sentiment = POZ - NEG) %>%
    select(word, dejt, sentiment) %>% 
    group_by(word) %>% 
    mutate(count = n()) %>%
    arrange(desc(count)) %>%
    mutate( score = sentiment*count) %>%
    ungroup() %>%
    group_by(dejt) %>%
    arrange(desc(dejt)) -> sm
  
  
  
  
  sm %>%
    select(dejt, score) %>%
    group_by(Datum = floor_date(dejt, "quarter")) %>%
    summarise(Tjedni_sent = sum(score, na.rm = TRUE)) %>%
    ggplot(., aes(Datum, Tjedni_sent)) +
    geom_bar(stat = "identity")+
    labs(title="",
         x ="Date", y = "Sentiment Score") -> gg_sentiment_kroz_vrijeme_qv
  
  
  #grid.arrange(gg_sentiment_kroz_vrijeme_qv, nrow = 2 )
  
  
}

fullCorpus <- izracunaj_sentiment(korpus_words)

fullCorpus #+ ggtitle("Graph X: Sentiment through time (quarterly) for full text corpus")

```

---
  layout: true
# SENTIMENT ANALYSIS

---
  
  <br>
  ## Uber text corpus
  <br>
  
```{r, echo=FALSE,  message = FALSE, warning = FALSE , fig.height=5 }

uberCorpus <- izracunaj_sentiment(uber_words)

uberCorpus #+ ggtitle("Graph X: Sentiment through time (quarterly) for Uber text corpus")

```


---
  layout: true
# SENTIMENT ANALYSIS

---
  
  <br>
  ## Conflict text corpus
  <br>
  
  
  ```{r , echo=FALSE,  message = FALSE, warning = FALSE, fig.height=5 }
sukobCorpus <- izracunaj_sentiment(sukob_words)

sukobCorpus #+ ggtitle("Graph X: Sentiment through time (quarterly) for conflict text corpus")
```



---
  
  layout:false
class: middle, inverse
# Thank you for your attention! 
<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>
  (Ovdje se može još nekaj dodati!?)

