---
title: "THE MEDIA'S PERSPECTIVE OF UBER'S DISRUPTION OF TAXI INDUSTRY IN CROATIA"
# subtitle: "<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>"
subtitle: "Sharing Cultures: 7th International Workshop on the Sharing Economy, Barcelona "
author: "Filip Majetic and Luka Sikic"
date: "Institute for Social Sciences Ivo Pilar | [Repository link](https://github.com/lusiki/TaxiDisruption)" #"`r format(Sys.time(), '%d %B %Y')`"
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts] 
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---


class: inverse, middle

```{R, setup, include = F}
# devtools::install_github("dill/emoGG")
library(pacman)
p_load(
  broom, tidyverse,
  latex2exp, ggplot2, ggthemes, ggforce, viridis, extrafont, gridExtra,
  kableExtra, snakecase, janitor,
  data.table, dplyr, estimatr,
  lubridate, knitr, parallel,
  lfe,
  here, magrittr
)
# Define pink color
red_pink <- "#e64173"
turquoise <- "#20B2AA"
orange <- "#FFA500"
red <- "#fb6107"
blue <- "#2b59c3"
green <- "#8bb174"
grey_light <- "grey70"
grey_mid <- "grey50"
grey_dark <- "grey20"
purple <- "#6A5ACD"
slate <- "#314f4f"
# Dark slate grey: #314f4f
# Knitr options
opts_chunk$set(
  comment = "#>",
  fig.align = "center",
  fig.height = 7,
  fig.width = 10.5,
  warning = F,
  message = F
)
opts_chunk$set(dev = "svg")
options(device = function(file, width, height) {
  svg(tempfile(), width = width, height = height)
})
options(crayon.enabled = F)
options(knitr.table.format = "html")
# A blank theme for ggplot
theme_empty <- theme_bw() + theme(
  line = element_blank(),
  rect = element_blank(),
  strip.text = element_blank(),
  axis.text = element_blank(),
  plot.title = element_blank(),
  axis.title = element_blank(),
  plot.margin = structure(c(0, 0, -0.5, -1), unit = "lines", valid.unit = 3L, class = "unit"),
  legend.position = "none"
)
theme_simple <- theme_bw() + theme(
  line = element_blank(),
  panel.grid = element_blank(),
  rect = element_blank(),
  strip.text = element_blank(),
  axis.text.x = element_text(size = 18, family = "STIXGeneral"),
  axis.text.y = element_blank(),
  axis.ticks = element_blank(),
  plot.title = element_blank(),
  axis.title = element_blank(),
  # plot.margin = structure(c(0, 0, -1, -1), unit = "lines", valid.unit = 3L, class = "unit"),
  legend.position = "none"
)
theme_axes_math <- theme_void() + theme(
  text = element_text(family = "MathJax_Math"),
  axis.title = element_text(size = 22),
  axis.title.x = element_text(hjust = .95, margin = margin(0.15, 0, 0, 0, unit = "lines")),
  axis.title.y = element_text(vjust = .95, margin = margin(0, 0.15, 0, 0, unit = "lines")),
  axis.line = element_line(
    color = "grey70",
    size = 0.25,
    arrow = arrow(angle = 30, length = unit(0.15, "inches")
  )),
  plot.margin = structure(c(1, 0, 1, 0), unit = "lines", valid.unit = 3L, class = "unit"),
  legend.position = "none"
)
theme_axes_serif <- theme_void() + theme(
  text = element_text(family = "MathJax_Main"),
  axis.title = element_text(size = 22),
  axis.title.x = element_text(hjust = .95, margin = margin(0.15, 0, 0, 0, unit = "lines")),
  axis.title.y = element_text(vjust = .95, margin = margin(0, 0.15, 0, 0, unit = "lines")),
  axis.line = element_line(
    color = "grey70",
    size = 0.25,
    arrow = arrow(angle = 30, length = unit(0.15, "inches")
  )),
  plot.margin = structure(c(1, 0, 1, 0), unit = "lines", valid.unit = 3L, class = "unit"),
  legend.position = "none"
)
theme_axes <- theme_void() + theme(
  text = element_text(family = "Fira Sans Book"),
  axis.title = element_text(size = 18),
  axis.title.x = element_text(hjust = .95, margin = margin(0.15, 0, 0, 0, unit = "lines")),
  axis.title.y = element_text(vjust = .95, margin = margin(0, 0.15, 0, 0, unit = "lines")),
  axis.line = element_line(
    color = grey_light,
    size = 0.25,
    arrow = arrow(angle = 30, length = unit(0.15, "inches")
  )),
  plot.margin = structure(c(1, 0, 1, 0), unit = "lines", valid.unit = 3L, class = "unit"),
  legend.position = "none"
)
theme_set(theme_gray(base_size = 20))
# Column names for regression results
reg_columns <- c("Term", "Est.", "S.E.", "t stat.", "p-Value")
# Function for formatting p values
format_pvi <- function(pv) {
  return(ifelse(
    pv < 0.0001,
    "<0.0001",
    round(pv, 4) %>% format(scientific = F)
  ))
}
format_pv <- function(pvs) lapply(X = pvs, FUN = format_pvi) %>% unlist()
# Tidy regression results table
tidy_table <- function(x, terms, highlight_row = 1, highlight_color = "black", highlight_bold = T, digits = c(NA, 3, 3, 2, 5), title = NULL) {
  x %>%
    tidy() %>%
    select(1:5) %>%
    mutate(
      term = terms,
      p.value = p.value %>% format_pv()
    ) %>%
    kable(
      col.names = reg_columns,
      escape = F,
      digits = digits,
      caption = title
    ) %>%
    kable_styling(font_size = 20) %>%
    row_spec(1:nrow(tidy(x)), background = "white") %>%
    row_spec(highlight_row, bold = highlight_bold, color = highlight_color)
}
```

```{css, echo = F, eval = F}
@media print {
  .has-continuation {
    display: block !important;
  }
}
```

```{r library, warning=FALSE, include=FALSE}

library(lubridate)
library(tidytext)
library(data.table)
library(wordcloud)
library(knitr)
library(gridExtra)
library(grid)
library(topicmodels)
library(stringr)
library(igraph)
library(ggraph)
library(kableExtra)
library(utils)
library(dplyr)
library(magrittr)
library(tidyr)
library(tufte)
library(scales)
library(ggthemes)
library(extrafont)
library(gridExtra)
library(stringi)
library(plm)
library(data.table)
library(gridExtra)
library(ggpubr)
library(knitr)
library(png)
library(widyr)
library(httr)
    
```

```{r import_Crosentilex, echo=FALSE,  message = FALSE, warning = FALSE}


CroSentilex_n <- read.delim("../Podatci/crosentilex-negatives.txt",
                                   header = FALSE,
                                   sep = " ",
                                   stringsAsFactors = FALSE,
                                   fileEncoding = "UTF-8")  %>%
                   rename(word = "V1", sentiment = "V2" ) %>%
                   mutate(brija = "NEG")
 
 CroSentilex_p  <- read.delim("../Podatci/crosentilex-positives.txt",
                                   header = FALSE,
                                   sep = " ",
                                   stringsAsFactors = FALSE,
                                   fileEncoding = "UTF-8") %>%
                    rename(word = "V1", sentiment = "V2" ) %>%
                    mutate(brija = "POZ")
 
 Crosentilex_sve <- rbind(setDT(CroSentilex_n), setDT(CroSentilex_p))
 
 
 CroSentilex_Gold  <- read.delim2("../Podatci/gs-sentiment-annotations.txt",
                                 header = FALSE,
                                 sep = " ",
                                 stringsAsFactors = FALSE) %>%
                    rename(word = "V1", sentiment = "V2" ) 

 Encoding(CroSentilex_Gold$word) <- "UTF-8"
 CroSentilex_Gold[1,1] <- "dati"
 CroSentilex_Gold$sentiment <- str_replace(CroSentilex_Gold$sentiment , "-", "1")
 CroSentilex_Gold$sentiment <- str_replace(CroSentilex_Gold$sentiment , "\\+", "2")
 CroSentilex_Gold$sentiment <- as.numeric(unlist(CroSentilex_Gold$sentiment))
 
 
 
 
 stopwords_cro <- get_stopwords(language = "hr", source = "stopwords-iso")
my_stop_words <- tibble(
  word = c(
    "jedan",
    "e","prvi", "dva","dvije","drugi",
    "tri","treći","pet","kod",
    "ove","ova",  "ovo","bez",
    "evo","oko",  "om", "ek",
    "mil","tko","šest", "sedam",
    "osam",   "čim", "zbog",
    "prema", "dok","zato", "koji", 
    "im", "čak","među", "tek",
    "koliko", "tko","kod","poput", 
    "baš", "dakle", "osim", "svih", 
    "svoju", "odnosno", "gdje",
    "kojoj", "ovi", "toga",
     "ubera", "vozača", "hrvatskoj", "usluge", "godine", "više", "taksi", "taxi", "taksija", "taksija", "kaže", "rekao"
  ),
  lexicon = "lux"
)
stop_corpus <- my_stop_words %>%
  bind_rows(stopwords_cro)


```

```{r import_Data, echo=FALSE,  message = FALSE, warning = FALSE}

taxi <- read.csv2("D:/Luka/Academic/Majetic_Uber/R_project_taxi/Podatci/TaksiFinalData.csv", stringsAsFactors = FALSE)  %>%
  mutate(dejt = as.Date(dejt, "%d.%m.%Y" ), 
         grupa_1 = toupper(grupa_1)) %>%      
  arrange(dejt) %>%
  filter(!duplicated(idClanka))

# Napravi automatski
out <- read.csv2("D:/Luka/Academic/Majetic_Uber/R_project_taxi/Podatci/13_visak.csv", stringsAsFactors = FALSE, header = FALSE) 

out %>% 
  mutate(id = str_extract("/\\d+", V2)) -> aa
#  str_extract("/\\d+", V2)
#.[str_detect(., "/\\d+")]

out <- c(1244111, 1244334, 1244587, 1247674, 1255495, 1256587, 1256489, 1257518, 1260218, 1260650, 1269678, 1252506, 1252259 )

`%notin%` <- Negate(`%in%`)


taxi <- taxi %>% filter(idClanka %notin% out)


```

```{r define_Data, echo=FALSE,  message = FALSE, warning = FALSE}

sukob <- taxi %>%
  filter(sukob %in% c("trad" , "kont" , "repo" , "sukob" ,  "kont2"))


uber <- taxi %>%
  filter(uber == "uber")


sukob_words <- taxi %>%
  filter(sukob %in% c("trad" , "kont" , "repo" , "sukob" ,  "kont2")) %>%
  unnest_tokens(word, tekst) %>%
  anti_join(stop_corpus, by = "word") %>%
  mutate(word = gsub("\\d+", NA, word)) %>%
  mutate(word = gsub("^[a-zA-Z]$", NA, word)) %>%
  filter(!is.na(word))

uber_words <- taxi %>%
  filter(uber == "uber") %>%
  unnest_tokens(word, tekst) %>%
  anti_join(stop_corpus, by = "word") %>%
  mutate(word = gsub("\\d+", NA, word)) %>%
  mutate(word = gsub("^[a-zA-Z]$", NA, word)) %>%
  filter(!is.na(word))

korpus_words <- taxi %>%
  unnest_tokens(word, tekst) %>%
  anti_join(stop_corpus, by = "word") %>%
  mutate(word = gsub("\\d+", NA, word)) %>%
  mutate(word = gsub("^[a-zA-Z]$", NA, word)) %>%
  filter(!is.na(word))

```




## INTRODUCTION

---
layout: true
# INTRODUCTION
---
<br>
<br>
<br>

-Official repository can be accessed on the [link](https://github.com/lusiki/TaxiDisruption).


---
layout: false
class: middle, inverse

# RESEARCH CONTEXT
---
layout: true
# RESEARCH CONTEXT
---
<br>
<br>
<br>

Here we explain what this is all about.




---
layout: false
class: middle, inverse

# METHODOLOGY AND DATA
---
layout: true
# MEDODOLOGY AND DATA
---
<br>
<br>
<br>

Methods used and how we got the data.


---
layout: false
class: middle, inverse

# INSIGHTS AND TOPIC IDENTIFICATION
---

layout: true
# INSIGHTS AND TOPIC IDENTIFICATION

---

### Unigrams

```{r unigram_Words, echo=FALSE,  message = FALSE, warning = FALSE}

korpus_words %>% 
  count(word) %>%
  arrange(desc(n)) %>%
  mutate(ratio = (n / sum(n))*100) %>%
  mutate(ratio = round(ratio,2)) %>%
  mutate(ratio = paste0(ratio,"%")) %>%
  filter(n > 100) %>%
  arrange(desc(n))  -> corpus

# ENGLESKI

corpus %>% 
    mutate(words = recode(word,
                         'prijevoza' = "transport",
                         'taksisti' = "taxi drivers",
                         "uber" = "uber",
                         "taksista" = "taxi drivers",
                        "vozila"  = "vehicles",
                        "zakona" = "law"  ,
                        "kuna"  = "kuna" ,
                        "prijevoz" = "transport",
                        "zagrebu" = "zagreb",
                        "prometa" = "traffic" ,
                        "vozači" = "drivers",
                        "uberu" = "uber" ,
                        "usluga" = "service"
                         )) %>%
  select(words,n,ratio) %>%
  rename(Word = words, N = n, Ratio = ratio) %>%
  distinct(.,Word,.keep_all = T) -> corpus
  
  


kable(corpus) %>% # , caption = "Table X: Most frequent words (>100)"
  kable_styling() %>%
  scroll_box(width = "500px", height = "300px")


```


---
layout: true
# INSIGHTS AND TOPIC IDENTIFICATION

---

### Bigrams


```{r bigram_Words, echo=FALSE,  message = FALSE, warning = FALSE}



##BIGRAMI FULL

bigrami <- function(dataset){

dataset %>%
  unnest_tokens(bigram, tekst, token = "ngrams", n = 2) %>%
  count(bigram, sort = TRUE) -> taxi_bigram 


bigrams_separated <- taxi_bigram %>%
  separate(bigram, c("word1", "word2"), sep = " ")

bigrams_filtered <- bigrams_separated %>%
  filter(!word1 %in% stop_corpus$word) %>%
  filter(!word2 %in% stop_corpus$word) %>%
  filter(!grepl("\\d+", word1)) %>%
  filter(!grepl("\\d+", word2)) %>% 
  filter(!grepl("^[a-zA-Z]$", word1)) %>%
  filter(!grepl("^[a-zA-Z]$", word2)) 

# new bigram counts:
bigram_counts <- bigrams_filtered %>% 
  count(word1, word2, sort = TRUE)

bigrams_united <- bigrams_filtered %>%
  unite(bigram, word1, word2, sep = " ")

bigrams_united %>%
  arrange(desc(n)) %>%
  mutate(ratio = (n / sum(n))*100) %>%
  mutate(ratio = round(ratio,2)) %>%
  mutate(ratio = paste0(ratio,"%")) %>%
  filter(n > 25) -> UniBigram 

}



#bigrami(uber)


CountBigram <- bigrami(taxi)

CountBigram %>%
    mutate(Bigram = recode(bigram,
                         'cestovnom prometu' = "road traffic",
                         'mora prometa' = "sea traffic",
                         'milijuna kuna' = "milion kuna",
                         'novog zakona' = "new law")) %>%
  rename(N=n, Ratio = ratio) %>%
  select(Bigram, N, Ratio) %>%
  kable(.) %>% kable_styling() # , caption = "Most frequent bigrams (>25)"
                         
  

#bigrami(sukob)

```


---
layout: true
# INSIGHTS AND TOPIC IDENTIFICATION

---

### The most correlated words (*with:*)


```{r corrs_corpus, echo=FALSE,  message = FALSE, warning = FALSE, fig.height=6}


rijeci_korelacija <- c("konkurencija", "nelegalno", "dozvola", "zakon","zarada", "profit", "sigurnost")


# korelacije

korpus_words %>%
  select(idClanka, word, sukob) %>%
  pairwise_count(word, idClanka, sort = TRUE) -> korpus_word_pairs

# vrijeme

korpus_word_pairs %>%
  filter(item2 %in% rijeci_korelacija) %>% 
  group_by(item2) %>%
  slice(1:5) %>%
  ungroup()  %>%
  mutate(item1 = recode(item1,
                         'prijevoza' = "transport",
                         'taksisti' = "taxi drivers",
                         "uber" = "uber",
                         "taksista" = "taxi drivers",
                        "vozila"  = "vehicles",
                        "zakona" = "law"  ,
                        "kuna"  = "kuna" ,
                        "prijevoz" = "transport",
                        "zagrebu" = "zagreb",
                        "prometa" = "traffic" ,
                        "vozači" = "drivers",
                        "uberu" = "uber" ,
                        "usluga" = "service",
                        "mora" = "must",
                        "može" = "can",
                        "prijevoza" = "traffic",
                        "uberu" = "uber",
                        "smatraju" = "consider",
                        "protiv" = "against",
                        "kažu" = "claim",
                        "prijevozu" = "traffic",
                        "tržište" = "market")) %>%
  mutate(item2 = recode(item2,
                        'zarada' = "income",
                         'sigurnost' = "safety",
                         'zakon' = "law",
                         "uber" = "uber",
                        "vozila"  = "vehicles",
                        "zakona" = "law",
                        "dozvola"  = "licence" ,
                        "konkurencija" = "competition",
                        "nelegalno" = "illegal" )) %>%
  mutate(item2 = reorder(item2, n)) %>%
  ggplot(aes(item1, n)) +
  geom_bar(stat = "identity") +
  facet_wrap(~ item2, scales = "free") +
  coord_flip() +
  labs(title="",
        x ="Word", y = "Number of words")

```


```{r additionals, eval = FALSE, echo = FALSE, fig.height=12}


rijeci <- c("novac", "plaća", "profit", "promet", "zapošljavanje", "sigurnost", "nesreće", "ozljeda", "zarada", "dobit")

korpus_word_pairs %>%
  filter(item2 %in% rijeci) %>% 
  group_by(item2) %>%
  slice(1:15) %>%
  ungroup() %>%
  mutate(item2 = reorder(item2, n)) %>%
  ggplot(aes(item1, n)) +
  geom_bar(stat = "identity") +
  facet_wrap(~ item2, scales = "free") +
  coord_flip() +
  ggtitle("Most correlated words with:")




korpus_words %>%
  mutate(Datum = floor_date(dejt, "quarter")) %>% 
  group_by(Datum) %>%
  count(word) %>% 
  mutate(gn = sum(n)) %>% 
  filter(word %in% rijeci) %>%
  ggplot(., aes(Datum, n / gn)) + 
  geom_point() +
  ggtitle("Most important terms through time(corpus conflict)") +
  geom_smooth() +
  facet_wrap(~ word, scales = "free_y") +
  scale_y_continuous(labels = scales::percent_format())



# bigrami

taxi %>%
unnest_tokens(bigram, tekst, token = "ngrams", n = 2) %>%
  count(bigram, sort = TRUE) -> taxi_bigram 


bigrams_separated <- taxi_bigram %>%
  separate(bigram, c("word1", "word2"), sep = " ")

bigrams_filtered <- bigrams_separated %>%
  filter(!word1 %in% stop_corpus$word) %>%
  filter(!word2 %in% stop_corpus$word) %>%
  filter(!grepl("\\d+", word1)) %>%
  filter(!grepl("\\d+", word2)) %>% 
  filter(!grepl("^[a-zA-Z]$", word1)) %>%
  filter(!grepl("^[a-zA-Z]$", word2)) 

# new bigram counts:
bigram_counts <- bigrams_filtered %>% 
  count(word1, word2, sort = TRUE)

bigrams_united <- bigrams_filtered %>%
  unite(bigram, word1, word2, sep = " ")

bigrams_united %>%
  arrange(desc(n)) %>%
  mutate(ratio = (n / sum(n))*100) %>%
  mutate(ratio = round(ratio,2)) %>%
  mutate(ratio = paste0(ratio,"%")) %>%
  filter(n > 25) %>%
  kable(.) %>% kable_styling() 

bigrams_filtered %>%
  filter(word1 %in% rijeci) %>% kable(.)

bigrams_filtered %>%
  filter(word2 %in% rijeci) %>% kable(.)

bigrams_filtered %>%
  filter(word1 == "sigurnost")

bigrams_filtered %>%
  filter(word2 == "sigurnost")

bigrams_filtered %>%
  filter(word2 == "ozljeda")

```

---
layout: true
# INSIGHTS AND TOPIC IDENTIFICATION

---

### Time dynamics of most common words (*full corpus*)

```{r time_corpus , echo=FALSE,  message = FALSE, warning = FALSE, fig.height=6}

korpus_words %>%
  mutate(Datum = floor_date(dejt, "quarter")) %>% 
  group_by(Datum) %>%
  count(word) %>% 
  mutate(gn = sum(n)) %>% 
  filter(word %in% rijeci_korelacija) %>%
  mutate(word = recode(word,
                         'sigurnost' = "safety",
                         'zakon' = "law",
                         "uber" = "uber",
                        "vozila"  = "vehicles",
                        "zakona" = "law",
                        "dozvola"  = "licence" ,
                        "konkurencija" = "competition",
                        "nelegalno" = "illegal",
                        "zarada" = "profit")) %>%
  ggplot(., aes(Datum, n / gn)) + 
  geom_point() +
  geom_smooth() +
  facet_wrap(~ word, scales = "free_y") +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(title="",
        x ="Date", y = "% of total words(quarterly)")



```



---
layout: false
class: middle, inverse

# RESULTS AND DISCUSSION
---

layout: true
# RESULTS AND DISCUSSION
---
<br>
## Corpus conflict (unigrams)
<br>
```{r unigram_Words_conflict,  echo=FALSE}

#uber_words %>% 
# count(word) %>%
#  arrange(desc(n)) %>%
#  top_n(30) -> uber_corpus

#kable(uber_corpus,
#                        caption = "Najčešće riječi u UBER korpusu") %>%
#  kable_styling() %>%
#  scroll_box(width = "500px", height = "300px")


sukob_words %>% 
  count(word) %>%
  arrange(desc(n)) %>%
  mutate(ratio = (n / sum(n))*100) %>%
  mutate(ratio = round(ratio,2)) %>%
  mutate(ratio = paste0(ratio,"%")) %>%
  filter(n > 100) %>%
  mutate(Word = recode(word,
                         'sigurnost' = "safety",
                         'zakona' = "law",
                         "uber" = "uber",
                        "vozila"  = "vehicles",
                       'taksisti' = "taxi drivers",
                       'taksista' = "taxi drivers")) %>%
  distinct(.,Word,.keep_all = T) %>%
  rename( N = n, Ratio = ratio) %>%
  select(Word,N,Ratio)-> sukob_corpus



kable(sukob_corpus) %>% # ,caption = "Table X: Most frequent words (>100)"
  kable_styling() 

```

---

layout: true
# RESULTS AND DISCUSSION
---
<br>
## Corpus conflict (bigrams)
<br>

```{r bigram_Words_conflict,  echo=FALSE}

sukobBigr <- bigrami(sukob)


sukobBigr %>%
    mutate(Bigram = recode(bigram,
                         'cestovnom prometu' = "road traffic",
                         'mora prometa' = "sea traffic",
                         'milijuna kuna' = "milion kuna",
                         'novog zakona' = "new law")) %>%
  rename(N=n, Ratio = ratio) %>%
  select(Bigram, N, Ratio) %>%
  kable(.) %>% kable_styling() # , caption = "Most frequent bigrams (>25)"

```


---

layout: true
# RESULTS AND DISCUSSION
---

### Most correlated words (*with selected important words from corpus "conflict"*)

```{r parwiseCount_conflict, echo=FALSE,  message = FALSE, warning = FALSE, fig.height=6}

###PARWISE COUNT###

# prikazuju se samo tri riječi prve

sukob_words %>%
  select(idClanka, word, sukob) %>%
  pairwise_count(word, idClanka, sort = TRUE) -> sukob_word_pairs


# sukob_words %>%
#  select(sukob, word) %>%
#  mutate(sukob = case_when(sukob == "trad" ~ 1,
#            sukob == "kont" ~ 2,
#            sukob == "kont2" ~3,
#            sukob == "repo" ~ 4)) %>%
#  mutate(sukob = as.integer(sukob)) %>% #str()
#  pairwise_count(word, sukob, sort = TRUE) -> sukob_word_pairs_sukob


sukob_rijeci <- c("prijedlog", "prosvjed", "prijetnje", "napad" ) # šteta
uber_rijeci <- c("posao", "zarada", "koristi", "cijena", "plaćanje")
korpus_rijeci <- c("zakon", "nelegalno", "politika", "ministar","turizam", "sigurnost")

##PARWISE COUNT SA IZABRANIM RIJEČIMA##



sukob_word_pairs %>%
  filter(item2 %in% sukob_rijeci) %>% 
  group_by(item2) %>%
  slice(1:4) %>%
  ungroup() %>%
  mutate(item1 = recode(item1,
                         'prijevoza' = "transport",
                         'taksisti' = "taxi drivers",
                         "uber" = "uber",
                         "taksista" = "taxi drivers",
                        "vozila"  = "vehicles",
                        "zakona" = "law"  ,
                        "kuna"  = "kuna" ,
                        "prijevoz" = "transport",
                        "zagrebu" = "zagreb",
                        "prometa" = "traffic" ,
                        "vozači" = "drivers",
                        "uberu" = "uber" ,
                        "usluga" = "service",
                        "mora" = "must",
                        "može" = "can",
                        "prijevoza" = "traffic",
                        "uberu" = "uber",
                        "smatraju" = "consider",
                        "protiv" = "against",
                        "kažu" = "claim",
                        "prijevozu" = "traffic",
                        "tržište" = "market",
                        "imaju" = "have",
                        "infrastrukture" = "infrastructure")) %>%
  mutate(item2 = recode(item2,
                         'napad' = "attack",
                         'prijedlog' = "suggestion",
                         "prijetnje" = "threats",
                        "prosvjed"  = "demonstrations" )) %>%
  mutate(item2 = reorder(item2, n)) %>%
  ggplot(aes(item1, n)) +
  geom_bar(stat = "identity") +
  facet_wrap(~ item2, scales = "free") +
  coord_flip() +
  labs(title="",
        x ="Word", y = "Number of words") 

```


---

layout: true
# RESULTS AND DISCUSSION
---


### Most important terms through time (*quarterly;corpus conflict*). 

```{r time_Words, echo=FALSE,  message = FALSE, warning = FALSE, fig.height=5   } 



sukob_words %>%
  mutate(Datum = floor_date(dejt, "quarter")) %>% 
  group_by(Datum) %>%
  count(word) %>% 
  mutate(gn = sum(n)) %>% 
  filter(word %in% sukob_rijeci) %>%
  mutate(word = recode(word,
                         'napad' = "attack",
                         'prijetnje' = "threats",
                         "prijedlog" = "suggestion",
                        "prosvjed"  = "demonstrations")) %>%
  ggplot(., aes(Datum, n / gn)) + 
  geom_point() +
  geom_smooth() +
  facet_wrap(~ word, scales = "free_y") +
  scale_y_continuous(labels = scales::percent_format())+
  labs(title="",
        x ="Date", y = "% of total words(quarterly)")

```


```{r, eval=FALSE, echo=FALSE,  message = FALSE, warning = FALSE }
uber_words %>%
  mutate(Datum = floor_date(dejt, "quarter")) %>% 
  group_by(Datum) %>%
  count(word) %>% 
  mutate(gn = sum(n)) %>% 
  filter(word %in% uber_rijeci) %>%
  ggplot(., aes(Datum, n / gn)) + 
  geom_point() +
  ggtitle("Korpus Uber") +
  geom_smooth() +
  facet_wrap(~ word, scales = "free_y") +
  scale_y_continuous(labels = scales::percent_format())


korpus_words %>%
  mutate(Datum = floor_date(dejt, "quarter")) %>% 
  group_by(Datum) %>%
  count(word) %>% 
  mutate(gn = sum(n)) %>% 
  filter(word %in% korpus_rijeci) %>%
  ggplot(., aes(Datum, n / gn)) + 
  geom_point() +
  ggtitle("Korpus") +
  geom_smooth() +
  facet_wrap(~ word, scales = "free_y") +
  scale_y_continuous(labels = scales::percent_format())


```


---
layout: false
class: middle, inverse

# TOPIC ANALYSIS
---
layout: true
# TOPIC ANALYSIS

---

### Most important words by topic

```{r IDF,echo=FALSE,  message=FALSE, warning=FALSE, fig.height=8}


sukob_words %>%
  count(sukob, word, sort = TRUE) %>%
  bind_tf_idf(word, sukob, n) -> idf_sukob

options(scipen = 1000000)
idf_sukob %>%
    mutate(word = factor(word, levels = rev(unique(word)))) %>% 
    group_by(sukob) %>% 
    select(sukob, word, tf_idf) %>%
    arrange(desc(tf_idf)) %>% 
    do(head(., n = 20)) %>% 
    filter(!word %in% c("tremac", "davor", "nekih", "ovdje",
                        "franković", "grabar", "kitarović",
                        "trebao", "martina", "ivan", "ribić", "pilko"))   %>%
  mutate(word = recode(word,
                         'dojam' = "impression",
                         'korisne' = "usefull",
                         "ispitanih" = "surveyed",
                         "odgovorilo" = "answered",
                        "policijskoj"  = "police",
                        "prijetnjama" = "threats"  ,
                        "regulativa"  = "regulation" ,
                        "verbalnom" = "verbal",
                        "žale" = "complain",
                        "napada" = "attack" ,
                        "dubrovačko" = "dubrovnik",
                        "nasilja" = "violence" ,
                        "usluga" = "service",
                        "opasnost" = "danger",
                        "partnerima" = "partners",
                        "pozitivna" = "positive",
                        "prošlih" = "historic",
                        "relikt" = "relict",
                        "štete" = "damage",
                        "prijedloga" = "proposal",
                        "naknadu" = "compensation",
                        "zakone" = "law",
                        'cestama' = "road",
                         'provodi' = "implement",
                         "pismu" = "letter",
                         "predstavnike" = "representative",
                        "primjedbi"  = "complaints",
                        "usluga" = "service"  ,
                        "ovlasti"  = "authority" ,
                        "umjesto" = "insteda",
                        "direktive" = "directives",
                        "dodatne" = "additional" ,
                        "dovodi" = "bring",
                        "interesu" = "interest" ,
                        'izvješća' = "report",
                         'mirnim' = "peacefull",
                         "prekršajni" = "criminal",
                         "općine" = "county",
                        "italiji"  = "italy",
                        "propisano" = "prescribed"  ,
                        "visoki"  = "high" ,
                        "usluga" = "service",
                        "javni" = "public",
                        "prijedloga" = "suggestion" ,
                        "optužni" = "indictment",
                        "prijavu" = "notification" ,
                        "list" = "paper",
                        "odbio" = "revoke",
                        "večernji" = "night",
                        'inspekcija' = "inspection",
                         'prijedlog' = "suggestion",
                         "aplikacija" = "application",
                         "troškovi" = "costs",
                        "napad"  = "attack",
                        "gotovo" = "over"  ,
                        "automobil"  = "car" ,
                        "sati" = "hours",
                        "policiji" = "police",
                        "potom" = "after" ,
                        "staklo" = "glass",
                        "ubacili" = "throw into" ,
                        "institucijama" = "institutions",
                        'normalno' = "normal",
                         'potpredsjednik' = "vice president",
                         "spontano" = "spontaneous",
                         "taxija" = "taxi",
                        "automobilu"  = "car" )) %>%
    ggplot(.,aes(reorder(word,tf_idf), tf_idf, fill = sukob)) +
    geom_col(show.legend = FALSE) +
    facet_wrap(~sukob, ncol = 2, scales = "free") +
    coord_flip() +
    labs(title="",
        x ="Word", y = "TF-IDF statistic") -> gg_idf_1

gg_idf_1

```


---
layout: false
class: middle, inverse

# SENTIMENT ANALYSIS
---
layout: true
# SENTIMENT ANALYSIS

---


<br>
## Full text corpus
<br>

```{r sentiment, echo=FALSE,  message = FALSE, warning = FALSE, fig.height=5 }

##SENTIMENT_FUNKCIJA

izracunaj_sentiment <- function(dataset) {

dataset %>%
  inner_join( Crosentilex_sve, by = "word") %>%
  mutate(word = gsub("\\d+", NA, word)) %>%
  mutate(word = gsub("^[a-zA-Z]$", NA, word)) %>%
  filter(!is.na(word)) %>%
  select(word, brija, dejt, sentiment) %>% 
  unique() %>%
  spread(. , brija, sentiment) %>%
  mutate(sentiment = POZ - NEG) %>%
  select(word, dejt, sentiment) %>% 
  group_by(word) %>% 
  mutate(count = n()) %>%
  arrange(desc(count)) %>%
  mutate( score = sentiment*count) %>%
  ungroup() %>%
  group_by(dejt) %>%
  arrange(desc(dejt)) -> sm

 
  

sm %>%
  select(dejt, score) %>%
  group_by(Datum = floor_date(dejt, "quarter")) %>%
  summarise(Tjedni_sent = sum(score, na.rm = TRUE)) %>%
  ggplot(., aes(Datum, Tjedni_sent)) +
  geom_bar(stat = "identity")+
  labs(title="Graph X: Sentiment through time (quarterly)",
        x ="Date", y = "Sentiment Score") -> gg_sentiment_kroz_vrijeme_qv


#grid.arrange(gg_sentiment_kroz_vrijeme_qv, nrow = 2 )


}

fullCorpus <- izracunaj_sentiment(korpus_words)

fullCorpus #+ ggtitle("Graph X: Sentiment through time (quarterly) for full text corpus")

```

---
layout: true
# SENTIMENT ANALYSIS

---

<br>
## Uber text corpus
<br>

```{r, echo=FALSE,  message = FALSE, warning = FALSE , fig.height=5 }

uberCorpus <- izracunaj_sentiment(uber_words)

uberCorpus #+ ggtitle("Graph X: Sentiment through time (quarterly) for Uber text corpus")

```


---
layout: true
# SENTIMENT ANALYSIS

---

<br>
## Conflict text corpus
<br>


```{r , echo=FALSE,  message = FALSE, warning = FALSE, fig.height=5 }
sukobCorpus <- izracunaj_sentiment(sukob_words)

sukobCorpus #+ ggtitle("Graph X: Sentiment through time (quarterly) for conflict text corpus")
```



---

layout:false
class: middle, inverse
# Thank you for your attention! 
<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>
(Ovdje se može još nekaj dodati!?)





















